Sample size

### 2021-05-03 scripts/r/sample-size/sample-size.Rmd
:bug: - set seed at beginning

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
theme_set(theme_light(base_family = "Lato"))
library(brms)
library(extraDistr)
library(HDInterval)
library(tidybayes)
my_seed <- 99
```

@@

  meta_bm <- brms::brm(
    z_score ~
      (1 | team),
    data = data,
    prior = priors,
    chain = 4,
    iter = 6000,
    cores = 4,
    seed = my_seed,
    backend = "cmdstanr", threads = brms::threading(4),
    control = list(adapt_delta = 0.9999, max_treedepth = 15),
  )

@@

```{r plot, eval=FALSE}
sample_sims <- sample_sims %>%
  mutate(
    cri = map(sd_team, function(.x) .x$random$team[4] - .x$random$team[3]) %>% unlist()
  )

labels <- tibble(
  x = c(0.5, 0.25, 0.9, 0.3, 1.3),
  y = c(1.25, 0.7, 1.5, 0.1, 0.8),
  labs = c("Mean", "1st quart.", "3rd quart.", "Min", "Max")
)

arrows <- tibble(
    x1 = c(0.5, 0.25, 0.9, 0.25, 1.3),
    y1 = c(1.15, 0.6, 1.4, 0.1, 0.9),
    x2 = c(0.63, 0.33, 0.97, 0.05, 1.33),
    y2 = c(0.8, 0.45, 1.2, 0.1, 1.1)
  )

sample_sims %>%
  ggplot(aes(quants, cri)) +
  geom_line(aes(colour = as.factor(n_teams))) +
  geom_point(aes(colour = as.factor(n_teams)), size = 4) +
  geom_hline(yintercept = 1) +
  geom_hline(yintercept = 2, linetype = "dashed") +
  geom_text(
    data = labels, aes(x, y, label = labs),
    family = "Lato"
  ) +
  geom_curve(
    data = arrows, aes(x = x1, y = y1, xend = x2, yend = y2),
    arrow = arrow(length = unit(0.07, "inch")), size = 0.4,
    color = "gray20", curvature = 0.3
  ) +
  scale_x_continuous(breaks = round(quantiles, 2)) +
  scale_color_manual(values = c("#bfd3e6", "#9ebcda", "#8c96c6", "#8c6bb1", "#88419d", "#6e016b")) +
  labs(
    title = "95% CrI width depending on teams' true SD and number of teams",
    x = "Teams' true standard deviation",
    y = "95% CrI width",
    colour = "N of teams",
    caption = "The values on the x-axis are the quartiles (0, 0.25, 0.5, 0.75, 1)\nof the estimated teams' SD from Silberzahn et al."
  )

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
theme_set(theme_light(base_family = "Lato"))
library(brms)
library(extraDistr)
library(HDInterval)
library(tidybayes)
my_seed <- 99
set.seed(my_seed)
```

@@

  meta_bm <- brms::brm(
    z_score ~
      (1 | team),
    data = data,
    prior = priors,
    chain = 4,
    iter = 6000,
    cores = 4,
    backend = "cmdstanr", threads = brms::threading(4),
    control = list(adapt_delta = 0.9999, max_treedepth = 15),
  )

@@

```{r plot}
sample_cri <- sample_sims %>%
  unnest(sd_team) %>%
  mutate(sd_team = unlist(sd_team)) %>% 
  filter(sd_team > 0) %>%
  rename(cri = sd_team)

labels <- tibble(
  x = c(0.5, 0.25, 0.9, 0.3, 1.3),
  y = c(1.25, 0.7, 1.5, 0.1, 1.15),
  labs = c("Mean", "1st quart.", "3rd quart.", "Min", "Max")
)

arrows <- tibble(
    x1 = c(0.5, 0.25, 0.9, 0.25, 1.3),
    y1 = c(1.15, 0.6, 1.4, 0.1, 1.2),
    x2 = c(0.63, 0.33, 0.97, 0.05, 1.33),
    y2 = c(0.8, 0.45, 1.2, 0.1, 1.39)
  )

sample_cri %>%
  ggplot(aes(quants, cri)) +
  geom_line(aes(colour = as.factor(n_teams))) +
  geom_point(aes(colour = as.factor(n_teams)), size = 4) +
  geom_hline(yintercept = 1) +
  geom_hline(yintercept = 2, linetype = "dashed") +
  geom_text(
    data = labels, aes(x, y, label = labs),
    family = "Lato"
  ) +
  geom_curve(
    data = arrows, aes(x = x1, y = y1, xend = x2, yend = y2),
    arrow = arrow(length = unit(0.07, "inch")), size = 0.4,
    color = "gray20", curvature = 0.3
  ) +
  scale_x_continuous(breaks = round(quantiles, 2)) +
  scale_color_manual(values = c("#e0ecf4", "#bfd3e6", "#9ebcda", "#8c96c6", "#8c6bb1", "#88419d", "#810f7c", "#4d004b")) +
  labs(
    title = "95% CrI width depending on teams' true SD and number of teams",
    x = "Teams' true standard deviation",
    y = "95% CrI width",
    colour = "N of teams",
    caption = "The values on the x-axis are the quartiles (0, 0.25, 0.5, 0.75, 1)\nof the estimated teams' SD from Silberzahn et al."
  )
